---
title: "Assignment 5-B Answers"
subtitle: "Version 1.0.0"
author: "Tim Crowe"
output: github_document
---

+ __Leader__: Victor Yuan
+ __Reviewer__: Diana Lin & Vincenzo Coia
+ __Deadline__: Saturday, December 12, 2020 at 23:59 PST

+ __Total Points__: 20 

## Option A -- Strings in R

Complete the following two exercises using concepts and tools covered in class (i.e. `stringr`, regex, tidyverse, etc.)

### Exercise 1 (9 points)

_Take a Jane Austen book contained in the `janeaustenr` package, or another book from some other source. Make a plot of the most common words in the book, removing "stop words" of your choosing (words like "the", "a", etc.) or stopwords from a pre-defined source, like the `stopwords` package or `tidytext::stop_words`._

```{r include = FALSE}

library(janeaustenr)
library(stopwords)
library(tidyverse)

```

I will be analysing the book "Emma" by Jane Austen to find the most common words. For the "stop words", I will use the `stopwords` package.

The `janeaustenr` package provides a character vector which contains the entire text of the novel "Emma" (along with her other novels). In order to do the analysis on this novel, I will remove all punctuation and change all upper case characters to lower case.

I will then create a tibble in which every single word in the novel is it's own row, and remove all the words contained in the list mentioned previously in order to show what the most common words in the novel are.

Step by step annotations of what I am doing is provided in the code:

```{r}

# use stopwords package and take default list of words to remove from the results
stopwords_list <- stopwords(language = "en", source = "snowball", simplify = TRUE)

# remove punctuation and convert all letters to lower case
emma_words_simplified <- emma %>%
  str_remove_all("[^ a-zA-Z]") %>%
  str_to_lower()

# create tibble for dplyr analysis
emma_tibble <- enframe(emma_words_simplified, value = "Text")

# modify tibble to get desired list of most common words in the book
emma_common_words <- emma_tibble %>%
  separate_rows(Text, sep = " ") %>% # make each word in text be it's own row
  rename(Word = Text) %>%
  filter(Word %in% stopwords_list == FALSE) %>% # remove words from the stoplist
  filter(Word != "") %>% # remove empty entries
  count(Word) %>%
  arrange(desc(n))

```

Now we have a tibble of all the unique words in the novel, except those found in `stopwords_list`, in descending order from most common to least. A plot of the 30 most common words follows:

```{r}

emma_common_words %>%
  top_n(30) %>%
  ggplot(aes(x = reorder(Word, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(y = "# Occurences", x = "") +
  theme_bw()

```

### Exercise 2 (9 points)

_Make a function that converts words to your own version of Pig Latin._

_The specific input and output that you decide upon is up to you. Don't forget to implement good function-making hygiene: we'll be looking for documentation (being sure to describe your Pig Latin conversion), examples of applying the function, 3 non-redundant tests, appropriate use of arguments, and appropriate amount of checking for proper input._

_Your Pig Latin should incorporate two components:_

**Rearrangement component** 

_The default Pig Latin rearrangement rule, [as per Wikipedia](https://en.wikipedia.org/wiki/Pig_Latin#Background), moves beginning letters to the end:_

> 1. For words that begin with consonant sounds, all letters before the initial vowel are placed at the end of the word sequence.
> 2. When words begin with consonant clusters (multiple consonants that form one sound), the whole sound is added to the end
> 3. For words beginning with vowel sounds, one removes the initial vowel(s) along with the first consonant or consonant cluster.

_Modify this somehow. Maybe you move letters from the end to the beginning, or you change the rules altogether, keeping a similar level of complexity._

**Addition component**

_The default Pig Latin addition rule is to add "ay" to the end of the word, after rearranging the letters of the word. You should choose some other addition rule._




```{r}

### STANDARD PIG LATIN

input = "spring"

word <- str_to_lower(input)
vowel_pos <- str_locate(word, "[aeiouAEIOU]")[1]
{if (vowel_pos == 1) 
  paste0(word, "way") 
  else 
  paste0(str_sub(word, vowel_pos, -1), str_sub(word, 1, vowel_pos - 1), "ay")}
       

```

```{r}

### NEW PIG LATIN

input = "water"

word <- str_to_lower(input)

# shift vowels up
word <- gsubfn(".", list("a" = "e", "e" = "i", "i" = "o", "o" = "u", "u" = "a"), word)

# find location of first vowel
vowel_pos <- str_locate(word, "[aeiouAEIOU]")[1]

# if word starts with vowel, add "yay" to end
# if word starts with consonant, move first consonant cluster (until first vowel) to end and add "nay"
{if (vowel_pos == 1) 
  paste0(word, "way") 
  else 
  paste0(str_sub(word, vowel_pos, -1), str_sub(word, 1, vowel_pos - 1), "ay")}
       

```

ERRORS

* numbers
* more than one word (ie includes punctuation or " " --- error [^a-zA-Z])

WARNING

* lower case
