---
title: "Assignment 5-B Answers"
subtitle: "Version 1.0.0"
author: "Tim Crowe"
output: github_document
---

+ __Leader__: Victor Yuan
+ __Reviewer__: Diana Lin & Vincenzo Coia
+ __Deadline__: Saturday, December 12, 2020 at 23:59 PST

+ __Total Points__: 20 

## Option A -- Strings in R

Complete the following two exercises using concepts and tools covered in class (i.e. `stringr`, regex, tidyverse, etc.)

### Exercise 1 (9 points)

_Take a Jane Austen book contained in the `janeaustenr` package, or another book from some other source. Make a plot of the most common words in the book, removing "stop words" of your choosing (words like "the", "a", etc.) or stopwords from a pre-defined source, like the `stopwords` package or `tidytext::stop_words`._

```{r include = FALSE}

library(janeaustenr)
library(stopwords)
library(tidyverse)

```


```{r}

stopwords_list <- stopwords(language = "en", source = "snowball", simplify = TRUE)
emma_words <- str_c(emma, collapse = " ")

```

```{r}

emma_words_unique <- emma_words %>%
  str_remove_all("[^ a-zA-Z]") %>% # remove all punctuation
  str_to_lower() %>% 
  str_split(" ") %>%
  .[[1]] %>%
  unique()

```
```{r}

emma_words_unique[emma_words_unique]

```

### Exercise 2 (9 points)

_Make a function that converts words to your own version of Pig Latin._

_The specific input and output that you decide upon is up to you. Don't forget to implement good function-making hygiene: we'll be looking for documentation (being sure to describe your Pig Latin conversion), examples of applying the function, 3 non-redundant tests, appropriate use of arguments, and appropriate amount of checking for proper input._

_Your Pig Latin should incorporate two components:_

**Rearrangement component** 

_The default Pig Latin rearrangement rule, [as per Wikipedia](https://en.wikipedia.org/wiki/Pig_Latin#Background), moves beginning letters to the end:_

> 1. For words that begin with consonant sounds, all letters before the initial vowel are placed at the end of the word sequence.
> 2. When words begin with consonant clusters (multiple consonants that form one sound), the whole sound is added to the end
> 3. For words beginning with vowel sounds, one removes the initial vowel(s) along with the first consonant or consonant cluster.

_Modify this somehow. Maybe you move letters from the end to the beginning, or you change the rules altogether, keeping a similar level of complexity._

**Addition component**

_The default Pig Latin addition rule is to add "ay" to the end of the word, after rearranging the letters of the word. You should choose some other addition rule._

